A Balanced Agent for Capture The Flag Pac-Man

### 2011-03-08 projectWriteup/paper.tex
Added the introduction to the paper
Note that when using pdflatex to compile paper.tex, to
get citations working, sometimes you have to compile like
2 or 3 times (since the bibliography is at the end and
LaTeX compiles unidirectionally).

\begin{document}
\maketitle
\section{Introduction}
Building a balanced Pac Man: the work of champions.

@@

>>>>

\begin{document}
\maketitle
\section{Introduction}
A popular and relevant field in artificial intelligence is noisy gameplay
\cite{miik}.  Noisy readouts, opposing agents, and limited calculation
time, mean that noisy games are open to a wide variety of AI techniques.
One particularly relevant example of this field is Capture the Flag (CTF)
Pac-Man, in which a team of independent agents tries to simultaneously
protect food on their side of a Pac-Man board while eating the food on
their opponents' side.  In this paper, we discuss our implementation of a
balanced agent to play CTF Pac-Man.
\\ \\
In our balanced agent, we observed that there are three main branches of
strategy in CTF Pac-Man: attacking, holding the line, and defending.  The
first attempts to eat opposing food, the second attempts to block opposing
agents from entering our side, and the third attempts to capture opposing
agents and prevent them from eating our food once they cross over.  We
built individual modules for each one of these strategies to recommend
moves.  As in many AI agents, the recommendations of these modules and the
global decision which module to apply use a combination of minimax and
expectimax, where we look several moves ahead, analyze the strength of our
position, and act accordingly.
\\ \\
Our differentiator and the primary focus of our work was on more advanced
ways to model opponents and determine the strength of a given game state,
as well as techniques to optimize the weights used to combine those
parameters into relevant state values.  For inference of opponent agent
positions, using prior knowledge and the noisy readings we could observe,
we used more than just sensor data, and incorporated a basic opponent
model.  Our various agents incorporated a wide variety of heuristics,
weighted to recommend moves.  We used a technique called Particle Swarm
Optimization (PSO) to find a string set of weights.  PSO tends to perform
well in functions like ours that are difficult to evaluate accurately and
impossible to analyze from a theoretical perspective \cite{carlisle}.
Furthermore, we observed that the best weightings varied between different
layouts.  Therefore, we trained weights for many different boards.  When
presented with a new board, we clustered it with similar boards (based on
a number of features of the layout) for which
we had trained values and used an average of those values.  The result is
an agent that has learned how to play well on a variety of different
layouts with a variety of different strategies, and combines that
knowledge effectively when presented with a new game.

\section{Heuristics}
\subsection{Offense}
\subsection{Defense}
\subsection{Hold the Line}

\section{Inference}

\section{Particle Swarm Optimization}
\subsection{Algorithm}
\subsection{Theoretical Justification}
\subsection{Performance and Results}

\section{$k$-means Clustering for Layouts}
To solve this problem of disparate weights selected by PSO for different
layouts, given a layout, we attempted to determine similar layouts for
which we had already computed training data.  To this end, we used
$k$-means cluatering.
\subsection{Methodology}
\subsection{Performance and Results}

\section{Overall Results}

\section{Discussion}

@@

\bibitem{miik} Miikkulainen, R. (2006) ``Creating Intelligent
  Agents in Games''.  {\it The Bridge}.  National Academy of Engineering.
